Multi-Instance Methods for Partially Supervised Image Segmentation

### 2013-09-22 intro.tex
citations for graz

In the following we distinguish between the task of semantic segmentation,
which usually distinguishes unstructured ``stuff'' classes such as road and
grass, and object class segmentation, which denotes the segmentation of very
structured classes, such as cars, planes and people. We consider four
different datasets in this thesis: the object class segmentation datasets
Graz02 and Pascal VOC 2010, and the semantic segmentation datasets MSRC-21, and
NYU V2.
%
Both tasks have the same ultimate goal of parsing, and therefore understanding,
images in terms of semantic classes. However they employ different mechanisms
to represent and process.

>>>>

In the following we distinguish between the task of semantic segmentation,
which usually distinguishes unstructured ``stuff'' classes such as road and
grass, and object class segmentation, which denotes the segmentation of very
structured classes, such as cars, planes and people. We consider four
different datasets in this thesis: the object class segmentation datasets
Graz-02~\citep{marszatek2007accurate} and Pascal VOC 2010~\citep{pascal}, and the semantic segmentation datasets
MSRC-21~\citep{shotton2006textonboost}, and NYU V2~\citep{SilbermanECCV12}.
%
Both tasks have the same ultimate goal of parsing, and therefore understanding,
images in terms of semantic classes. However they employ different mechanisms
to represent and process.

### 2013-09-22 partial_supervision/paper.tex
citations for graz

\subsection{Partially Supervised Image Segmentation on Graz 02}

We evaluate the performance of the proposed algorithm for object-class
segmentation on the challenging Graz-02 dataset.  This dataset contains 1096
images of three object classes, bike, car and person.  Each image may contain
multiple instances of the same class, but only one class is present per image.

@@

We evaluated the proposed object-class segmentation method on the challenging
Graz02 dataset. While not reaching the performance of methods using strong
supervision, our result can work as a baseline for further research into weakly
supervised object-class segmentation.

>>>>

\subsection{Partially Supervised Image Segmentation on Graz-02}

We evaluate the performance of the proposed algorithm for object-class
segmentation on the challenging Graz-02 dataset~\citep{marszatek2007accurate}.  This dataset contains 1096
images of three object classes, bike, car and person.  Each image may contain
multiple instances of the same class, but only one class is present per image.

@@

We evaluated the proposed object-class segmentation method on the challenging
Graz-02 dataset. While not reaching the performance of methods using strong
supervision, our result can work as a baseline for further research into weakly
supervised object-class segmentation.
